
\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{caption}
\usepackage{subfig}
\usepackage{url}
\usepackage{epstopdf}
%\usepackage{graphics,graphicx}
%\usepackage{cite}%
%\usepackage{epsfig}
\usepackage{array}
\usepackage{pifont}
\usepackage{multirow}
%\usepackage{fixltx2e}
\usepackage{amssymb}
\usepackage{footnote}
\usepackage{tablefootnote}
%\usepackage[utf8]{inputenc}
%\usepackage[TS1,T1]{fontenc}


%\usepackage[latin1]{inputenc}


% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}

%\setcopyright{rightsretained}  % this was un-commented originally - SG
\setcopyright{iw3c2w3}
% added by KH as per https://www.overleaf.com/14253237rhxnsnkxskbb#/54980477/


%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DOI
\acmDOI{10.1145/3184558.3191623}

% ISBN
\acmISBN{978-1-4503-5640-4/18/04}

%Conference
\acmConference[WWW'18 Companion]{The 2018 Web Conference Companion}{April 23--27, 2018}{Lyon, France}
\acmBooktitle{WWW'18 Companion: The 2018 Web Conference Companion, April 23--27, 2018, Lyon, France}
\acmYear{2018}
\copyrightyear{2018}
\acmPrice{}
% \bookTitle{The 2018 Web Conference Companion, April 23--27, 2018, Lyon, France}
%%%%%%%%%%%%%%%%%%%%%%%%%%%


\usepackage{color}
\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
\newcommand{\new}[1]{\textcolor{blue}{#1}}

\fancyhead{}

\begin{document}

\title{SAVITR: A System for Real-time Location Extraction from Microblogs during Emergencies}

\author{Ritam Dutt}
\affiliation{%
  \institution{Dept. of Computer Science and Engineering}
  \streetaddress{}
  \city{Indian Institute of Technology Kharagpur}
  \state{India}
  \postcode{721302}
}
\email{ritam@iitkgp.ac.in}

\author{Kaustubh Hiware}
\affiliation{%
  \institution{Dept. of Computer Science and Engineering}
  \streetaddress{}
  \city{Indian Institute of Technology Kharagpur}
  \state{India}
  \postcode{721302}
}
\email{hiwarekaustubh@iitkgp.ac.in}

\author{Avijit Ghosh}
\affiliation{%
  \institution{Dept. of Chemical and Financial Engineering}
  \streetaddress{}
  \city{Indian Institute of Technology Kharagpur}
  \state{India}
  \postcode{721302}
}
\email{avijitg22@iitkgp.ac.in}

\author{Rameshwar Bhaskaran}
\affiliation{%
  \institution{Dept. of Computer Science and Engineering}
  \streetaddress{}
  \city{Indian Institute of Technology Kharagpur}
  \state{India}
  \postcode{721302}
}
\email{rameshwar.cs@iitkgp.ac.in}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{R. Dutt et al.}


\begin{abstract}
\input{abstract}
\end{abstract}


%\if 0
%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
 \begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002951.10003317</concept_id>
<concept_desc>Information systems~Information retrieval</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information systems~Information retrieval}

%\fi

% We no longer use \terms command
%\terms{Theory}

\keywords{Emergencies, microblogs, location extraction, Geonames}


\maketitle

\input{source}


\section*{Acknowledgements} 
The authors thank Dr. Saptarshi Ghosh, Department of Computer Science and Engineering, IIT Kharagpur, for mentorship and guidance throughout the project. 
The authors acknowledge the annotators (Sohan Patro and others) who helped in evaluation of the methodologies, and useful discussions with Nishant Nikhil in the early stage of the project. 
The authors also thank the anonymous reviewers whose comments helped to improve the paper.
The work is partially supported by Microsoft Research India, and part of the work was done at the 2017 MSR India Summer Workshop on Artificial Social Intelligence.


\bibliographystyle{ACM-Reference-Format}
\bibliography{twitter_references,reference} 

\end{document}

